Eye-tracking on the web: lessons learned from replicating 5 experiments

### 2022-06-16 manuscript.Rmd
add study selection table #31

We chose five high-impact eyetracking studies involve adult subjects. (Given the additional difficulties of recruiting and retaining child participants, we excluded developmental studies.) Our goal was to include exempars from a range of topic areas (e.g., memory, decision-making, psycholinguistics) and paradigms (two
halves of the screen, visual world paradigm with four quadrants, visual
world paradigm with "natural" scenes). As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible.

The final selection of studies was FUBAR...

>>>>

<!-- June 2022: shimojo: 964 citations, altmann: 1840, ryskin: 75, johansson 190, 127 -->

We chose five high-impact eyetracking studies involving adult subjects. (Given the additional difficulties of recruiting and retaining child participants, we excluded developmental studies.) Our goal was to include experiments from a range of topic areas (e.g., memory, decision making, psycholinguistics) and paradigms (two
halves of the screen, visual world paradigm with four quadrants, visual
world paradigm with "natural" scenes). As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible. TABLE X provides an overview of the five studies we selected.

```{r Create Studies Table, echo=FALSE}
studies_table <- data.frame(
  Citation = c(
    "Altmann & Kamide, 1999",
    "Johansson & Johansson, 2013",
    "Manns, Stark, & Squire, 2000",
    "Ryskin et al., 2017",
    "Shimojo et al., 2003"
  ),
  `Topic Area` = c(
    "Psycholinguistics",
    "Memory",
    "Memory",
    "Psycholinguistics",
    "Decision Making"
  ),
  `Paradigm` = c(
    "Natural Scenes",
    "Four Quadrants",
    "Two Halves",
    "Four Quadrants",
    "Two Halves"
  ),
  `Citations (June 2022, Google Scholar)` = c(
    1840,
    190,
    127,
    75,
    964
  ),
  check.names = FALSE
)

apa_table(
  studies_table,
  caption = "Studies selected for replication attempts",
  font_size = "small"
)

### 2022-06-16 manuscript.tex
add study selection table #31

We chose five high-impact eyetracking studies involve adult subjects. (Given the additional difficulties of recruiting and retaining child participants, we excluded developmental studies.) Our goal was to include exempars from a range of topic areas (e.g., memory, decision-making, psycholinguistics) and paradigms (two
halves of the screen, visual world paradigm with four quadrants, visual
world paradigm with ``natural'' scenes). As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible.

The final selection of studies was FUBAR\ldots{}

>>>>

We chose five high-impact eyetracking studies involving adult subjects. (Given the additional difficulties of recruiting and retaining child participants, we excluded developmental studies.) Our goal was to include experiments from a range of topic areas (e.g., memory, decision making, psycholinguistics) and paradigms (two
halves of the screen, visual world paradigm with four quadrants, visual
world paradigm with ``natural'' scenes). As noted above, we had a preference for well-established findings that are known to replicate, though for sake of diversity this was not always possible. TABLE X provides an overview of the five studies we selected.

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:Create Studies Table}Studies selected for replication attempts}

\small{

\begin{tabular}{llll}
\toprule
Citation & \multicolumn{1}{c}{Topic Area} & \multicolumn{1}{c}{Paradigm} & \multicolumn{1}{c}{Citations (June 2022, Google Scholar)}\\
\midrule
Altmann \& Kamide, 1999 & Psycholinguistics & Natural Scenes & 1,840.00\\
Johansson \& Johansson, 2013 & Memory & Four Quadrants & 190.00\\
Manns, Stark, \& Squire, 2000 & Memory & Two Halves & 127.00\\
Ryskin et al., 2017 & Psycholinguistics & Four Quadrants & 75.00\\
Shimojo et al., 2003 & Decision Making & Two Halves & 964.00\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}
